---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CERFIT

<!-- badges: start -->
<!-- badges: end -->

The CERFIT R package is an implementation of Random Forest of Interaction Trees (RFIT) in R. Which is a modification of the random forest algorithm to estimate individualized treatment effect in randomized control trials and observational studies.

## Installation

You can install the development version of CERFIT from [GitHub](https://github.com/JustinThorp/CERFIT) with:

``` r
# install.packages("devtools")
devtools::install_github("JustinThorp/CERFIT")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example,eval=FALSE}
library(CERFIT)
fit <- CERFIT(y + x_1 + x_2 | t,
              data = data)
ite <- predict(fit,type = "ITE")
importance <- minDepth(fit)
```

